Patchwork: Incremental Computation for Static Analysis

### 2018-10-03 paper.tex
Finish first attempt at an analysis trace visualization

I also played around for a while with string substring operations (where we'd have to relate the length of the substring to the total length of the list and the beginning index to prove accesses safe) but couldn't come up with a clean simple example to work with.
\end{lstlisting}
\fi

>>>>

I also played around for a while with string substring operations (where we'd have to relate the length of the substring to the total length of the list and the beginning index to prove accesses safe) but couldn't come up with a clean simple example to work with.

\fi

\begin{table}[]
  \centering
  \newcommand{\location}{\tikz\draw[green!65!black,fill=green!65!black] (0,0) circle (.4ex);}
  \def\arraystretch{2}
    \begin{tabular}{r|l|ccl}
        \# & Program Location & \multicolumn{3}{l}{Analysis State Progression} \\
        \midrule
        1 & \texttt{x = 10;\location} &\quad&$\{\}$\tikzmark{1a} & \\
        \hline
        2 & \texttt{y = 0;\location} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{2a} & \hspace{1em}$\{x+y\leq10\}$\tikzmark{2b}\\
        \hline
        3 & \texttt{while(x > 0)\{\location} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{3a} & \tikzmark{3b}\\
        \hline
        4 & \quad\texttt{x--;\location} &$\bot$\quad&  $\{x+y\leq9\}$\tikzmark{4a}& \\
        \hline
        5 & \quad\texttt{if(*) \{y++;\location\}} &$\bot$\quad&$\{x+y\leq10\}$\tikzmark{5a}& \\
        \hline
        6 & \quad\texttt{else \{$\epsilon$;\location\}} &$\bot$\quad& $\{x+y\leq9\}$\tikzmark{6a} & \\
        \hline
        7 & \location\texttt{\}} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{7a} & \tikzmark{7b}\\
        \hline
%        8 & \qquad$\epsilon$ & $x+y\leq9$& \\
%        \hline
        8 & \location~\texttt{assert(x + y $\le$ 10)} &$\bot$\quad& $\{x+y\leq10\}$\tikzmark{8a} & \hspace{1em}$\{x+y\leq10\}$\tikzmark{8b}\\
    \end{tabular}

    \newcommand{\abovetext}{10pt}
    \newcommand{\belowtext}{-4pt}

    \begin{tikzpicture}[overlay,remember picture, shorten >=-3pt]
      \coordinate (1a) at ([xshift=-0.46em]pic cs:1a) ;
      \coordinate (2a) at (pic cs:2a);
      \coordinate (3a) at (pic cs:3a);
      \coordinate (4a) at (pic cs:4a);
      \coordinate (5a) at (pic cs:5a);
      \coordinate (6a) at (pic cs:6a);
      \coordinate (7a) at (pic cs:7a);
      \coordinate (8a) at (pic cs:8a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a) -- ([yshift = \abovetext]1a|-2a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-2a) -- ([yshift = \abovetext]1a|-3a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-3a) -- ([yshift = \abovetext]1a|-4a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-4a) -- ([yshift = \abovetext]1a|-5a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-4a)
      to [out=270,in=90] ([xshift=0.6em,yshift=0.2em] pic cs:5a)
      to [out=270,in=90] ([yshift = \abovetext]1a|-6a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-5a)
      to [out=270,in=90] ([xshift=-5.25em,yshift=0.25em] pic cs:6a)
      to [out=270,in=90] ([yshift = \abovetext]1a|-7a);
      \draw[->, blue!75!black] ([yshift=\belowtext]1a|-6a) -- ([yshift = \abovetext]1a|-7a);
      \draw[->, blue!75!black,rounded corners=4pt] ([yshift=4pt,xshift=1pt] pic cs:7a) -| ([xshift=-1pt] pic cs:3b) |- ([xshift=-5.5em, yshift=3pt]pic cs:2b);
      \draw[->, blue!75!black,rounded corners=4pt] ([yshift=4pt,xshift=1pt] pic cs:7a) -| ([yshift=-5pt, xshift=-1pt] pic cs:7b) |- ([xshift=-5.5em, yshift=3pt]pic cs:8b);
      \draw[->, blue!75!black,rounded corners=3pt] ([yshift=3pt,xshift=-5.25em] pic cs:2a) -| ([xshift=-5.65em,yshift=0.35em] pic cs:6a) |- ([yshift=3pt,xshift=-5.5em] pic cs:8a);
    \end{tikzpicture}

    \caption{ Visualization of fix-point computation for a program analyzer performing octagon analysis on the example program from Fig.~\ref{???}.
      Program locations in the abstract syntax are denoted by green circles in the concrete syntax.  The blue arrows illustrate a ``trace'' of the worklist/fix-point computation, showing the propagation of dataflow analysis results through the program.
%      Thus, the full history of partially-computed abstract states at a particular location is recorded from left to right in the ``Analysis State Progression'' column.
    }
    \label{tab:ATT}
\end{table}
